---
title: "Does giving information about labor market and migrant's education level affect the perceived skills transferability?"
author: "William Fernandez, Fernanda Gomes, Cintya Huaire"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output: rmdformats::downcute
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r, results='hide', message = FALSE, warning = FALSE}
library(tidyverse) # To use dplyr functions and the pipe operator when needed
library(ggplot2) # To visualize data
library(stargazer) # To format model output
library(modelsummary) # To customize the information displayed in your model summary tables
```

# Loading Dataset
```{r, results='hide', message = FALSE, warning = FALSE}
dta_experiment <- read.csv("final_data.csv", sep = ";")
```

# Processing Dataset
```{r, results='hide', message = FALSE, warning = FALSE}
##Cleaning
# excluding unfinished survey
attach(dta_experiment)
newdata <- dta_experiment[ which(FINISHED==1 ),]
detach(dta_experiment)

# removing 3 observations that were not assign to any group, and surveys without consent
newdata <- newdata[ which(newdata$IL02!=" " | newdata$C103 =="I agree"),]

#dropping observations of non students
newdata <- newdata[ which(newdata$A108!="No" ),]

##Transformation and creation of variables
#changing age into numeric
newdata$A101 <- as.numeric(newdata$A101)

#creating dummies for descriptive
#Can't be named Europe because people who are not from Europe have marked none of the above as an option
newdata$no_docs_req<- ifelse(newdata$A110=="None of the above", 1,0)

regressiondata <- newdata

#Fixing vars names 
regressiondata$age <- regressiondata$A101

regressiondata$country_birth <- regressiondata$A104

#creating dummies for regressions
regressiondata$dmale <- ifelse(regressiondata$A102 == "Male", 1,0)

regressiondata$dgerman <- ifelse(regressiondata$A104 == "Germany", 1,0)

regressiondata$dunemployed <- ifelse(regressiondata$A105 == "Unemployed", 1,0)

regressiondata$dwhite <- ifelse(regressiondata$A107 == "Caucasian/White",1,0)

regressiondata$dprivate <- ifelse(regressiondata$A109 == "Private",1,0)

regressiondata$dno_docs_req <- ifelse(regressiondata$A110 == "None of the above",1,0)

regressiondata$dcontrol <- ifelse(regressiondata$IL02 == "Control group", 1,0)

regressiondata$treatment1 <- ifelse(regressiondata$IL02 == "Group 1",1,0)

regressiondata$treatment2 <- ifelse(regressiondata$IL02 == "Group 2",1,0)

regressiondata$dG101_ca <- ifelse(regressiondata$G101 == "Completely agree" , 1, 0)

regressiondata$dG102_ca <- ifelse(regressiondata$G102 == "Completely agree" , 1, 0)

regressiondata$dG103_ca <- ifelse(regressiondata$G103 == "Completely agree" , 1, 0)

regressiondata$dG104_ca <- ifelse(regressiondata$G104 == "Completely agree" , 1, 0)

# transforming the outcome variables and the educ variable in factors
regressiondata$educ_level <- factor(regressiondata$A106, levels = c ("Master's Degree", "Bachelor's Degree", "High school"))

regressiondata$G101 <- factor(regressiondata$G101, levels=c("Completely agree","Somewhat agree", "Neither agree nor disagree", "Somewhat disagree", "Completely disagree"))

regressiondata$G102 <- factor(regressiondata$G102, levels = c("Completely agree","Somewhat agree", "Neither agree nor disagree", "Somewhat disagree", "Completely disagree"))

regressiondata$G103 <- factor(regressiondata$G103, levels = c("Completely agree","Somewhat agree", "Neither agree nor disagree", "Somewhat disagree", "Completely disagree"))

regressiondata$G104 <- factor(regressiondata$G104, levels = c("Completely agree","Somewhat agree", "Neither agree nor disagree", "Somewhat disagree", "Completely disagree"))

# selecting relevant variables to work it

regressiondata <- regressiondata %>% dplyr::select("age", "country_birth", "G101","G102", "G103", "G104", "dmale", "educ_level", "dgerman", "dunemployed", "dwhite", "dprivate", "dno_docs_req", "dcontrol", "treatment1", "treatment2", "dG101_ca", "dG102_ca", "dG103_ca", "dG104_ca")
```

# Descriptive

```{r, results='hide', message = FALSE, warning = FALSE}

ggplot(regressiondata, aes(x = G101, fill=G101)) + 
  geom_bar(alpha = 0.6) +
  theme_classic() +
  labs(title = "G101: Immigrants in Germany are well educated",
       x = "",
       y = "") + 
  theme(legend.position = "none")

ggsave("../distribution_g101.png")


ggplot(regressiondata, aes(x = G102, fill=G102)) + 
  geom_bar(alpha = 0.6) +
  theme_classic() +
  labs(title = "G102: Immigrants can apply their skills in the German labor market (PST)",
       x = "",
       y = "") + 
  theme(legend.position = "none")

ggsave("../distribution_g102.png")


ggplot(regressiondata, aes(x = G103, fill=G103)) + 
  geom_bar(alpha = 0.6) +
  theme_classic() +
  labs(title = "G103: Immigrants will increase competition in the labor market for me personally (L1)",
       x = "",
       y = "") + 
  theme(legend.position = "none",text = element_text(size=10))

ggsave("../distribution_g103.png")

ggplot(regressiondata, aes(x = G104, fill=G104)) + 
  geom_bar(alpha = 0.6) +
  theme_classic() +
  labs(title = "G104: In general, immigrants will increase competition in the labor market (L2)",
       x = "",
       y = "") + 
  theme(legend.position = "none",text = element_text(size=10))

ggsave("../distribution_g104.png")


#Distribution of age
regressiondata %>%
  dplyr::mutate(group_mean = mean(age)) %>% 
  dplyr::mutate(group_median = median(age)) %>%
ggplot(., aes(x = age)) + 
  geom_density(alpha = 0.5, fill="#FF6666") +
  geom_vline(aes(xintercept = group_mean), linetype = "longdash") + 
  geom_vline(aes(xintercept = group_median), linetype = "solid") +
  theme_classic() +
  theme(legend.position = "bottom", plot.caption=element_text(hjust=0)) +
  labs(title = "Distribution of age in the sample",
       x = "Age*",
       y = "", 
       caption = "*Solid line represents the median and dashed line, the mean.")

ggsave("../age.png")
```


# Balance Check 

<em>done in Stata as we had two treatments</em>

Code used:

<pre><code>
*Variables	
gen 				master = (educ_level==1)
gen 				bachelor = (educ_level==2)
gen 				high_school = (educ_level==3)
gen 				treatment_status = 1 if dcontrol==1
replace 			treatment_status = 2 if treatment1==1
replace 			treatment_status = 3 if treatment2==1

*Labels
label 				var age "Age"
label 				var dmale "Gender: male"
label 				var dgerman "Country of birth: Germany"
label 				var dunemployed "Unemployed"
label 				var dwhite "Ethnicity: white"
label 				var dprivate "Goes to private university"
label 				var dno_docs_req "Docs. required: none"
label 				var master "Highest level attained: Master"
label 				var bachelor "Highest level attained: Bachelor"
label 				var high_school "Highest level attained: High school"

global 				covariates age dmale dgerman dunemployed dwhite dprivate dno_docs_req master bachelor high_school

foreach var in $covariates {
				 
	mean     `var', over(treatment_status)
	
	matrix   a1=e(b)
	local 	 mean_control = a1[1,1]
	local 	 mean_T1 = a1[1,2]
	local 	 mean_T2 = a1[1,3]

	reg 	 `var' treatment1 treatment2
	
	local    p_diff_1 = (2 * ttail(e(df_r), abs(_b[treatment1]/_se[treatment1])))
	local    p_diff_2 = (2 * ttail(e(df_r), abs(_b[treatment2]/_se[treatment2])))
	
	lincom   treatment1 
	local 	 diff_C_T1 = r(estimate)
	
	lincom   treatment2
	local 	 diff_C_T2 = r(estimate)

  lincom   treatment2-treatment1
	local 	 diff_T1_T2 = r(estimate)
	local    sd_diff_T1_T2 = r(se)
  local    p_diff_T1_T2 = (2 * ttail(e(df_r), abs(`diff_T1_T2'/`sd_diff_T1_T2')))

	
	matrix   Balance_`var' = [ `mean_control', `mean_T1', `mean_T2', `diff_C_T1', `diff_C_T2', `diff_T1_T2'] 
	matrix   Stars_`var' = [0,0,0,0,0,0] 
  matrix   Stars_`var'[1,4]=(`p_diff_1'<=0.1)+(`p_diff_1'<=0.05)+(`p_diff_1'<=0.01) 
	matrix   Stars_`var'[1,5]=(`p_diff_2'<=0.1)+(`p_diff_2'<=0.05)+(`p_diff_2'<=0.01) 
	matrix   Stars_`var'[1,6]=(`p_diff_T1_T2'<=0.1)+(`p_diff_T1_T2'<=0.05)+(`p_diff_T1_T2'<=0.01) 

  matrix   Balance = [nullmat(Balance)\ Balance_`var']
	matrix   Stars = [nullmat(Stars)\Stars_`var']
	}


  frmttable using "$william\Output\Balance.tex", ///
	tex statmat(Balance) fragment				///
	ctitles("Variable", "Control", "T1", "T2", "T1 vs. C", "T2 vs. C", "T2 vs. T1") ///
	rtitles("Age" \ "Gender: male" \ "Country of birth: Germany" \ "Unemployed" \ "Ethnicity: white" \ ///
	"Goes to private university" \ "Docs. required: none" \  "Highest level attained: Master" \ ///
	"Highest level attained: Bachelor" \ "Highest level attained: High school") ///
	annotate(Stars) asymbol(*, **, ***) note("* p<0.1, ** p<0.05, *** p<0.01") replace 
	
	cap mat drop Balance Stars 
</code></pre>

# Regressions

```{r, results='hide', message = FALSE, warning = FALSE}
model_1 <- lm(G102 ~ treatment1 + treatment2, data=regressiondata)

model_2 <- lm(dG102_ca ~ treatment1 + treatment2, data=regressiondata)

model_3 <- lm(G103 ~ treatment1 + treatment2, data=regressiondata)

model_4 <- lm(dG103_ca ~ treatment1 + treatment2, data=regressiondata)

model_5 <- lm(G104 ~ treatment1 + treatment2, data=regressiondata)

model_6 <- lm(dG104_ca ~ treatment1 + treatment2, data=regressiondata)

stargazer::stargazer(model_1, model_2,
                     type = "latex",
                     report = ("vc*"),
                     title = "Effect of treatment on Perceived Skills Transferability",
                     model.numbers = FALSE,
                     covariate.labels = c("Treatment 1", "Treatment 2"),
                     dep.var.labels = c("PST-Factor", "PST-Dummy"),
                     dep.var.caption = "", 
                     omit.stat=c("rsq","adj.rsq","f","ser"))

stargazer::stargazer(model_3, model_4, model_5, model_6,
                     type = "latex",
                     report = ("vc*"),
                     title = "Effect of treatment on secondary outcomes",
                     model.numbers = FALSE,
                     covariate.labels = c("Treatment 1", "Treatment 2"),
                     dep.var.labels = c("L1-Factor", "L1-Dummy","L2-Factor","L2-Dummy"),
                     dep.var.caption = "", 
                     omit.stat=c("rsq","adj.rsq","f","ser"))


model_7 <- lm(dG103_ca ~ treatment1 + treatment2 + age + dmale + dgerman + dunemployed + dwhite + dprivate + dno_docs_req, data = regressiondata)

model_8 <- lm(dG103_ca ~ treatment1 + treatment2 + treatment2*age + age + dmale + dgerman + dunemployed + dwhite + dprivate + dno_docs_req, data = regressiondata)

model_9 <- lm(dG103_ca ~ treatment1 + treatment2 + treatment2*dunemployed + age + dmale + dgerman + dunemployed + dwhite + dprivate + dno_docs_req, data = regressiondata)


stargazer::stargazer(model_7, model_8, model_9,
                     type = "latex",
                     report = ("vc*"),
                     title = "Effect of treatment on L1: Immigrants will increase competition in the labor market for me personally",
                     model.numbers = FALSE,
                     dep.var.labels= "", 
                     covariate.labels = c("Treatment 1", "Treatment 2", "Age", "Male", "German", "Unemployed", "White", "Private univ.", "No docs. req."),
                     column.labels = c("Additive", "Interactive 1", "Interactive 2"),
                     dep.var.caption = "", 
                     omit = c("Constant"), 
                     omit.stat=c("rsq","adj.rsq","f","ser"))
```
